Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-12 paper.tex
Reference figure 10 for peak C_T metric; resolves #66
Add explicit algorithm to peak C_T metric; resolves #67

In conjunction with the cross-flow turbine blade kinematics, the foil
coefficients were used to approximate turbine performance by calculating the
peak torque coefficient on the upstream half of the blade path. The turbine
torque coefficient $C_T$ can be related to the blade section chordwise force
coefficient $C_c$ by
\begin{equation}
C_T = \frac{C_c c}{2R} \frac{|U_\mathrm{rel}|^2}{U_\infty^2},
\end{equation}
where the blade section chordwise force (for zero preset pitch) is given by
\begin{equation}
C_c = C_l \sin \alpha - C_d \cos \alpha.
\end{equation}

@@

From the peak torque coefficient metric, the Reynolds number independence is
achieved at lower values, and more dramatically. We see that the trend of the
(non-cambered) NACA 0020 curve matches almost perfectly up to $Re_c \approx 2.1
\times 10^5$, but then continues to increase linearly with a small slope with
$Re$. This is not matched by the experimental data, which at higher $Re$ looks
more like the cambered foil results. Though this method is very approximate, it
nevertheless appears to be a reasonable way to predict the transitional Reynolds
number regime for cross-flow turbine performance using only 2-D static airfoil
characteristics

@@

We propose a method for predicting Reynolds number dependence of a cross-flow
turbine using static airfoil characteristics and turbine blade kinematics. It is
shown that the peak torque coefficient computed this way shows similar Reynolds
number sensitivity---a better predictor than conventional quantifications of
airfoil performance, e.g., lift-to-drag ratio. The simple peak geometric torque
coefficient model predicted Reynolds number independence for Reynolds numbers
based on blade chord of $Re_c > 2 \times 10^5$. Is it also shown from this
metric that foils with higher camber are more Reynolds number dependent at lower
Reynolds number but have smaller slopes in the linear regime. The Reynolds
number dependence of the peak torque coefficient calculated from static foil
data and cross-flow turbine kinematics was shown to be a reasonable indicator
for predicting Reynolds number dependence of an actual cross-flow turbine
operating under dynamic conditions, including dynamic stall.

>>>>

In conjunction with the cross-flow turbine blade kinematics, the foil
coefficients were used to approximate turbine performance by calculating the
peak torque coefficient on the upstream half of the blade path. The turbine
torque coefficient $C_T$ can be related to the blade section chordwise force
coefficient $C_c$ by
\begin{equation}
C_T = \frac{C_c c}{2R} \frac{|U_\mathrm{rel}|^2}{U_\infty^2},
\label{eq:ct}
\end{equation}
where the blade section chordwise force (for zero preset pitch) is given by
\begin{equation}
C_c = C_l \sin \alpha - C_d \cos \alpha.
\label{eq:cc}
\end{equation}

@@

From the peak torque coefficient metric plotted in
Figure~\ref{fig:foils-C_T-Re-dep}, the Reynolds number independence is achieved
at lower values, and more dramatically. We see that the trend of the
(non-cambered) NACA 0020 curve matches almost perfectly up to $Re_c \approx 2.1
\times 10^5$, but then continues to increase linearly with a small slope with
$Re$. This is not matched by the experimental data, which at higher $Re$ looks
more like the cambered foil results. Though this method is very approximate, it
nevertheless appears to be a reasonable way to predict the transitional Reynolds
number regime for cross-flow turbine performance using only 2-D static airfoil
characteristics

@@

We propose a method for predicting Reynolds number dependence of a cross-flow
turbine using static airfoil characteristics and turbine blade kinematics:
\begin{enumerate}
    \item Acquire static lift and drag coefficient data for the desired blade
    profile.

    \item For azimuthal angles of 0--180 degrees and a given tip speed ratio,
    calculate the geometric angle of attack and relative velocity magnitude from
    the blade and undisturbed free stream velocity ($\equiv 1$) vectors.

    \item With arrays of geometric angle of attack and relative velocity
    magnitude, calculate the blade chordwise force and then rotor torque
    coefficient from Equations~\ref{eq:cc} and \ref{eq:ct}, respectively.

    \item Extract the maximum value of $C_T$, and repeat this process for static
    foil data at multiple $Re$.
\end{enumerate}

It was shown that the peak torque coefficient computed this way shows similar
Reynolds number sensitivity---a better predictor than conventional
quantifications of airfoil performance, e.g., lift-to-drag ratio. The simple
peak geometric torque coefficient model predicted Reynolds number independence
for Reynolds numbers based on blade chord of $Re_c > 2 \times 10^5$. Is it also
shown from this metric that foils with higher camber are more Reynolds number
dependent at lower Reynolds number but have smaller slopes in the linear regime.
The Reynolds number dependence of the peak torque coefficient calculated from
static foil data and cross-flow turbine kinematics was shown to be a reasonable
indicator for predicting Reynolds number dependence of an actual cross-flow
turbine operating under dynamic conditions, including dynamic stall.
